Group members: Lynn Huang, Prateek Oberoi, Aisha Washington 

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
av
```


```{r}
# A loop to get rid of all missing entries in final dataset

for (i in c(1:173))
{
  for (j in c(11,13,15,17,19))
  {
    if (av[i,j] != "YES" & av[i,j] != "NO" )
    {av[i,j] = NA}
  }
}

deaths = av %>% gather(key = Time, value = Deaths,na.rm=TRUE)
deaths = deaths %>% mutate(Time = parse_number(Time))
```

```{r}
Deaths.Final = saveRDS(deaths, "deaths.RDS")
```


# Investigation Questions 

# Lynn's Investigation Question

Lynn wanted to verify the quote "Of the nine Avengers we see on screen — Iron Man, Hulk, Captain America, Thor, Hawkeye, Black Widow, Scarlet Witch, Quicksilver and The Vision — every single one of them has died at least once in the course of their time Avenging in the comics. In fact, Hawkeye died twice!"

```{r}
Summary = deaths %>% filter(Name.Alias %in% c("Anthony Edward \"Tony\" Stark","Robert Bruce Banner","Thor Odinson","Steven Rogers","Clinton Francis Barton","Pietro Maximoff","Wanda Maximoff","Natalia Alianovna Romanova","Victor Shade (alias)")) %>% group_by(Name.Alias) %>% select(Name.Alias,Deaths,Time) %>% summarise( no.deaths = max(Time))

kable(Summary, caption = "Number of Deaths")
```
To determine whether or not this claim was true, I took a subset of all the main Avengers, then found out how many times each of them died. This claim happens to be true. Iron Man, Hulk, Captain America, Thor, Hawkeye, Black Widow, Scarlet Witch, Quicksilver and The Vision all have at least one recorded death, and Hawkeye (Clint) has two recorded deaths. 

# Aisha's Investigation Question

Aisha investigated whether the following statement was true:
"But you can only tempt death so many times. There’s a 2-in-3 chance that a member of the Avengers returned from their first 
stint in the afterlife, but only a 50 percent chance they recovered from a second or third death.""

```{r}
av3 <- deaths %>% gather(key = TimeR, value = Returns, c(11:15))
av3$TimeR <- parse_number(av3$TimeR)
av3 <- av3 %>% filter(Time == TimeR) %>% select(-TimeR)

# Filter to examine only deaths
av3 %>% filter(Deaths == 'YES') %>% 
  ggplot(aes(x = Returns)) +
  geom_bar() +
  facet_wrap(~Time)

# count of first deaths versus multiple deaths
av3 %>% filter(Time == 1)av3 %>% summarise(count(Time))
```

An avenger is more likely to return after one death than after two deaths.  
However, we also see that while many Avengers die once, much fewer die multiple deaths.
